Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov test in \proglang{R}

### 2021-06-17 journalMS/article.tex
RB minor edits, good to go

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}}
\Plaintitle{Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in R}
\Shorttitle{2-Dimensional Kolmogorov--Smirnov in \proglang{R}}

>>>>

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov test in \proglang{R}}
\Plaintitle{Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov test in R}
\Shorttitle{2-dimensional KS test in \proglang{R}}
